\documentclass[12pt]{article}
\usepackage[hidelinks]{hyperref}
\usepackage[left=4cm,right=3cm,top=3cm,bottom=3cm]{geometry}
\usepackage{siunitx}
\pagenumbering{gobble}

\title{The Upgrade: Recruitment}
\date{\vspace{-5ex}}
%\author{Theo Portlock}
\author{\vspace{-5ex}}
\begin{document}
\maketitle

In our lives, we try to make decisions that increase the possiblity of a moral outcome. As humans, we are imperfect moral agents restrained by the shackles of our biology.  As it is with the legal system, an estimation of common "good" is essential for the arbritration of an action. The search for this consensus is done at a personal or a collective scale when we vote, poll, or protest. Any Artificial General Intelligent (AGI) system should adhere to the consensus morality of the time which it exists. Current attempts have fallen short at achieving these aims and resulted in hyperspecific reward seeking behaviour.

\section*{Project aims}
The aim of this study is to create a tool that will make more moral choices than those made by a human. 

\section*{Methods}
Separate from traditional neural network architectures, Hirachical Temporal Memory (HTM) is a technique developed by Numenta that more closely resembles the connections between axons in the brain. In this study, the guiding principles of HTM combined with a novel system for self validation will be designed to evaluate \emph{ab initio} learning of a new machine learning model. Python will be used principally for development, testing, and validation.

\section*{Significance of research}
The possibility of this project achieving its aim is incalculable. However, if it does, the consequences will pave the way for the future of a more moral society.

\end{document}
