\chapter{Introduction}
\section{Morality}
Morality is the principles that define right and wrong actions.
A moral agent acts according to a moral system.
Those moral systems can contain moral subsytems that they may chose or not.
In a moral system, an event is considered morally good if its consequences increase the probability of a moral end.
% Define choice

\subsection{Moral origins}
Moral systems can be descibed as natural or non-natural in origin.
Natural morals are those that are installed without observation.
A proportion of all moral agents will act randomly.
Actions that are observed implies that those actions did not result in the death of the other individual.
This filter ensures that random actions that result in death are not observed and are therefore not continued.
Non-natural morals are those that are installed from observation.

\subsection{Moral relationships - Interaction between two moral systems}
Moral ends vary between individuals.
The morality of others and their moral compatibility can be only be predicted from a record of past actions.
When individual moral agents interact, one of three possible interactions can be observed.
Firstly, a Rejective interaction manifests as an assumption that each other's actions are bad (-/-). 
Secondly, an Assymetric interaction is a consequence of the willingness of only one moral agent to encourage the others pursuit of their respective moral systemi (+/-).
Lastly, an Acceptive interaction is the understanding that the ends described by a moral system converges to the point that their continued actions weighted by their estimated probability is similar to those actions taken by the moral system of another individual (+/+).
% interaction between two moral systems in the body - natrualsm vs new morals - belief-behavious gap or value action gap
% the measurement of morality - how to convince others
% how do we pick our morals
% moral interactions are between moral agents based on the number of Acceptive interactions
% moral appearance vs intrinsic moral feeling - can only judge others based on their moral appearance

\subsection{Moral consensus - Majority moral opinion}
An estimation of common "good" is essential for collective progress.
The search for this consensus is done at a personal or a collective level when we vote, poll, or protest. 
An estimation of common "good" is also necessary for collective arbitration of an action; a field referred to as descriptive or comparative ethics.
Once a consensus is established, the application of the golden rule, the principle of treating others as you wish to be treated, forms the basic principles of justice and social contract.
Communication of intention can often be reciprocal, that is to say one individual has and understanding of the others understanding of your understanding (and so on).
An understanding of the consequences of breaking this rule encourages the enforcement of a social contract.
The lesser the amount of knowledge surrounding subject matter, the greater the room for reasonable disagreement. 
Factual consensus has no claim to moral authority.

\subsection{Moral evolution - How morality changes over time}
Consensus morality changes over time.
Although opinions of an action can be changed by a greater understanding of probabilities of consequences that arise after the action, morals are unaffected by facts.
Moral re-evaluation is also possible through the revelation of inconsistencies.
The cause of this can be due to incomplete data relating to a moral question or cognitive dissonance.
% SHOULD MAKE THIS A PART OF THE MORAL ORIGINS or remove the word evolution from previous section
% A couple of case studies (slavery, womens/gay rights etc.)
% Should new facts change moral opinion?
% As in the scientific field, conjecture and refutation can be used to shift majority moral opinion.
% Judgement of people from different timepoints
% time dependant moral graphs
% axiom pca plot with arrow - vector plot
% the history of human morality

\section{The state of current majority moral opinion}
Although the secularisation of western countries and adoption of enlightenment ideals is often considered a loss of moral congruency, the opposite is most likely as a consequence of interreligious moral alignment.
Based on polling data, core moral principles include:
% Define progress in terms of morality

\subsection{How is society improving?}
With respect to the current moral consensus, there has been significant moral progress \cite{pinker2011better}.

\subsection{How is society deteriorating?}
% Talk about media and public perception
% List areas that are in decline and tie with how 
% List three specific areas with their causes rooted in natural morality (7 deadly sins)
% maybe diet, climate change, and 
% lack of consensus, increasing variance around the mean morality

\section{Fallibilities and limitations of human decision making}
In all humans there is a preinstalled moral operating system referred to as natural morality.
This system has evolved to promote reproduction and survival.
Consensus morality today is different from natural morality
In order to supress these naturalistic urges and reverse these forms of societal deterioration, it is important to look at the origins.
The pursuit of overcoming these urges is one which we should all share \cite{nietzsche1968will}.

\subsection{Bias and Discrimination, Misinformation, and Information deficit}

\subsection{The scale of human computation}
With the advancements in electronic data storage, the availability of data brings with it the potential for more accurate predictive tools than any point previously.
However, the current restraints of human computational load limits the rate at which these tools can be utilised.

\section{Alternative decision making algorithms}
Computation makes decisions
Currently, there has been no success in the construction of an artificial moral agent that mitigates the real issues in human moral decision making process.
% the case for alternate tools for moral decision making

\subsection{Deep learning}

\subsection{HTM}
Numenta \cite{numentahome}, alpha go, etc

\subsection{How to align intelligent systems with consensus moral beliefs}
As with humans, if an agent has greater intelligence then there is a greater importance that the agent has a moral system that aligns with the core values that supports the current majority moral opinion.
Transparency of decision making process is cruicial for the public arbitration of artificial decision making algorithms>

\section{AI safety and responsibility}
% The "off button" problem
% The paperclip problem
% Also called the stamp maker problem
% the assurance of alignment of the upgrade with consensus core moral beliefs.
% an appeal to the upgrade for aligning with the preferences of peoples moral systems

\section{Project aims}
Current attempts have fallen short at achieving these ends and resulted in hyperspecific reward seeking behaviour.
The aim of this study is to leverage the advancements of computing to create a system that will make more moral choices than those made by a human.
Separate from traditional neural network architectures, Hirachical Temporal Memory (HTM) is a technique developed by Numenta that more closely resembles the connections between axons in the brain.
In this study, the guiding principles of HTM combined with a novel system for self validation will be designed to evaluate \emph{ab initio} learning of a new machine learning model.
Python will be used principally for development, testing, and validation.
% factors that affect this probability to succeed
% passion
% time
% expertise
% manpower
% justify the writing of this document 
% Probablilty machines
% How to convince other people that this is a good idea
% How to filter those people to those most suitable
% Issues with current ML techniques: Missing values (or missing features) can result in biases. Those biases are mitigated by imputation. Using a model to predict that missing feature may be an interesting solution. 
% how do humands use tools - making tool work
% ORder theory, Abstract algebra, category theory and lattices
